## High-Speed Rial: A Seperate Situatiuon for the United States
# This R Markdown contains all the data cleaning and visualization code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mapdata)
library(ggplot2)
library(ggmap)
library(maps)
library(ggrepel)
library(osmdata)
library(sp)
library(raster)
library(sf)
library(spData)
library(tmap)
library(leaflet)
library(mapview)
library(shiny)
library(conflicted)
library(plotly)
library(RColorBrewer)
```

# set up conflicted functions
```{r}
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

# set color palette
palette(brewer.pal(n = 12, name = "Set3"))
```


# set up amtrak datasets
```{r}
seattleToLA <- read.csv("datasets/amtrak/seattleToLA.csv")
seattleToLA <- seattleToLA %>% 
  mutate(timeDate = as.POSIXct(timeDate, format = '%m/%d-%H:%M')) %>%
  add_column(animationFrame = 1:99)

laToSeattle <- read.csv("datasets/amtrak/laToSeattle.csv")
laToSeattle <- laToSeattle %>% 
  mutate(timeDate = as.POSIXct(timeDate, format = '%m/%d-%H:%M')) %>%
  add_column(animationFrame = 1:99)

coastStarlight <- rbind(seattleToLA, laToSeattle)

# get coast starlight route lat-long
amtrakRoutes <- read.csv("datasets/amtrak/amtrakRoutes.csv")
coastStarlightRoute <- amtrakRoutes %>% 
  filter(NAME == "Coast Starlight")

# get amtrak station info for lat/long
amtrakStations <- read.csv("datasets/amtrak/amtrakStations.csv")
westCoastStations <- amtrakStations %>% filter(STATE == "WA" | STATE == "OR" | STATE == "CA") %>%
  mutate_all(funs(tolower)) %>%
  mutate(urban = ifelse(urban == "yes", "yes", "no")) %>%
  mutate(CITY2 = ifelse(CITY2 == "eugene", "eugene-springfield", CITY2)) %>%
  mutate(CITY2 = ifelse(CITY2 == "oakland - jack london square", "oakland", CITY2)) %>%
  mutate(CITY2 = ifelse(CITY2 == "burbank bob hope airport", "burbank airport", CITY2)) %>%
  rename(stop = CITY2, lat = Y, long = X, stationCode = STNCODE, stateShort = STATE, fullStationName = STNNAME, urban = urban) %>% 
  mutate(lat = as.numeric(lat)) %>% 
  mutate(long = as.numeric(long)) %>% 
  select(lat, long, stationCode, stateShort, fullStationName, stop, urban)

# get the y-axis
yAxisStarlight <- coastStarlight %>%
  select(distanceKM, stop) %>%
  unique()
yAxisStarlight <- merge(yAxisStarlight, westCoastStations, by = "stop", all = FALSE, sort = FALSE) %>% 
                  select(stop, distanceKM, stationCode)

# get the population information for the city where station resides
westCoastStationsPopulation <- read.csv("datasets/amtrak/westCoastStationPopulation.csv")
westCoastStationsPopulation <- westCoastStationsPopulation %>% 
                               rename(stop = station) %>%
                               select(stop, city, state, pop)

# merge information
westCoastStationInformation <- merge(westCoastStations, westCoastStationsPopulation, by = "stop", all = FALSE, sort = FALSE)
westCoastStationComplete <- merge(westCoastStationInformation, yAxisStarlight %>% select(stop, distanceKM), by = "stop", all = FALSE, sort = FALSE)


# only larger cities where population is greater than 200,000 people
westCoastLargePop <- westCoastStationComplete %>% 
                     filter(pop > 200000)
coastStarlightLargePop <- coastStarlight %>% filter(stop %in% westCoastLargePop$stop)
yAxisStarlightLargePop <- coastStarlightLargePop %>%
  select(distanceKM, stop) %>%
  unique()

# first coast starlight of the week
seattleToLAMiniOne <- seattleToLA %>% slice(1:33)
laToSeattleMiniOne <- laToSeattle %>% slice(1:33)
coastStarlightMiniOne <- rbind(seattleToLAMiniOne, laToSeattleMiniOne)

# second coast starlight of the week
seattleToLAMiniTwo <- seattleToLA %>% slice(34:66)
laToSeattleMiniTwo <- laToSeattle %>% slice(34:66)
coastStarlightMiniTwo <- rbind(seattleToLAMiniTwo, laToSeattleMiniTwo)

# third coast starlight of the week
seattleToLAMiniThree <- seattleToLA %>% slice(67:99)
laToSeattleMiniThree <- laToSeattle %>% slice(67:99)
coastStarlightMiniThree <- rbind(seattleToLAMiniThree, laToSeattleMiniThree)
```

## plot amtrak stations on map using ggplot2 polygons
```{r}
# whole west coast
westCoastMap <- map_data("state") %>% filter(region == "washington" | region == "oregon" | region == "california") 
westCoastPlot <- ggplot() + 
                 geom_polygon(data = westCoastMap, aes(x = long, y = lat, group = group), 
                              color = "black", fill = "white") + coord_fixed() +
                 geom_point(data = westCoastStationComplete, aes(x = long, y = lat, color = state, label = stop, size = pop), 
                            shape = 20) +
                 theme_void() + 
                 labs(x = "",
                       y = "",
                       title = "Amtrak Coast Starlight Stations") +
                 theme(plot.title = element_text(hjust = 0.5),
                       legend.position = "") +
                 scale_color_brewer(palette = "Dark2")
westCoastPlot 
ggplotly(westCoastPlot, tooltip = c("label", "size", "x", "y")) %>% plotly::layout(legend = list(x = 0.1, y = 0.9))

# west coast large cities
westCoastPlotLarge <- ggplot() + 
                 geom_polygon(data = westCoastMap, aes(x = long, y = lat, group = group), 
                              color = "black", fill = "white") + coord_fixed() +
                 geom_point(data = westCoastLargePop, aes(x = long, y = lat, color = state, size = pop), 
                            shape = 20) +
                 theme_void() + 
                 geom_label_repel(data = westCoastLargePop, 
                            aes(x = long, y = lat, label = city), 
                            hjust = 0, vjust = 0, color = "darkred", size = 2,
                            box.padding = 0.20, point.padding = .2) + 
                  labs(x = "",
                       y = "",
                       title = "Amtrak Coast Starlight Stations") +
                  theme(plot.title = element_text(hjust = 0.5),
                        legend.position = "")+
                 scale_color_brewer(palette = "Dark2")


# plot washington amtrak stations
#OSM CALL
washingtonGGMap <- get_map(getbb("Washington State United States"), maptype = "terrain", source = "osm")
washingtonRail <- getbb("Washington State United States") %>%
  opq(timeout = 20*100) %>%
  add_osm_feature(key = "railway", value = "rail") %>%
  osmdata_sf()

washingtonMap <- map_data("state") %>% filter(region == "washington") 
washingtonPlot <- ggplot() + 
                  geom_polygon(data = washingtonMap, aes(x = long, y = lat, group = group), 
                              color = "black", fill = "white") + 
                  coord_fixed() +
                  geom_sf(data = washingtonRail$osm_lines,
                            inherit.aes = FALSE,
                            color = "lightgrey",
                            size = .5,
                            alpha = .6) +
                  geom_point(data = westCoastStationComplete %>% filter(state == "washington"), aes(x = long, y = lat), 
                            shape = 20, color = "darkred", size = 2) +
                  geom_label_repel(data = westCoastStationComplete %>% filter(state == "washington"), 
                            aes(x = long, y = lat, label = city), 
                            hjust = 1, vjust = 1, color = "darkred", size = 4,
                            box.padding = 0.10, point.padding = .2,
                            label.size = NA, fill = alpha(c("white"), 0.1), direction = "x") +
                  theme_void() +   
                  labs(x = "",
                       y = "",
                       title = "Amtrak Coast Starlights Stations in Washington") +
                  theme(plot.title = element_text(hjust = 0.5),
                        legend.position = "")

# oregon amtrak stations
#OSM CALL
oregonGGMap <- get_map(getbb("Oregon State United States"), maptype = "terrain", source = "osm")
oregonRail <- getbb("Oregon State United States") %>%
  opq(timeout = 20*100) %>%
  add_osm_feature(key = "railway", value = "rail") %>%
  osmdata_sf()

oregonMap <- map_data("state") %>% filter(region == "oregon") 
oregonPlot <- ggplot() + 
                  geom_polygon(data = oregonMap, aes(x = long, y = lat, group = group), 
                              color = "black", fill = "white") + 
                  coord_fixed() +
                  geom_sf(data = oregonRail$osm_lines,
                            inherit.aes = FALSE,
                            color = "lightgrey",
                            size = .5,
                            alpha = .6) +
                  theme_void() +   
                  labs(x = "",
                       y = "",
                       title = "Amtrak Coast Starlight Stations in Oregon") +
                  theme(plot.title = element_text(hjust = 0.5),
                        legend.position = "") +
                  geom_point(data = westCoastStationComplete %>% filter(state == "oregon"), aes(x = long, y = lat), 
                            shape = 20, color = "darkred", size = 2) +
                  geom_label_repel(data = westCoastStationComplete %>% filter(state == "oregon"), 
                            aes(x = long, y = lat, label = city), 
                            hjust = 1, vjust = 1, color = "darkred", size = 4,
                            box.padding = 0.20, point.padding = .2, label.size = NA, fill = alpha(c("white"), 0.1), direction = "x")

# california amtrak stations
#OSM CALL
californiaGGMap <- get_map(getbb("California State United States"), maptype = "terrain", source = "osm")
californiaRail <- getbb("California State United States") %>%
  opq(timeout = 20*100) %>%
  add_osm_feature(key = "railway", value = "rail") %>%
  osmdata_sf()

californiaMap <- map_data("state") %>% filter(region == "california") 
californiaPlot <- ggplot() + 
                  geom_polygon(data = californiaMap, aes(x = long, y = lat, group = group), 
                              color = "black", fill = "white") + 
                  coord_fixed() +
                  geom_sf(data = californiaRail$osm_lines,
                            inherit.aes = FALSE,
                            color = "lightgrey",
                            size = .5,
                            alpha = .6) +
                  geom_point(data = westCoastStationComplete %>% filter(state == "california"), aes(x = long, y = lat), 
                            shape = 20, color = "darkgreen", size = 2) +
                  geom_label_repel(data = westCoastStationComplete %>% filter(state == "california"), 
                            aes(x = long, y = lat, label = stop), 
                            hjust = 1, vjust = 0, color = "darkred", size = 2.5,
                            box.padding = 0.20, point.padding = .2, direction = "y", nudge_x = filter(westCoastStationComplete, state == "california")$long - 10,
                            segment.size = 0.2, fill = alpha(c("white"), 0.1), label.size = NA) +
                  theme_void() +   
                  labs(x = "",
                       y = "",
                       title = "Amtrak Coast Starlight Stations in California") +
                  theme(plot.title = element_text(hjust = 0.5),
                        legend.position = "")
```

## [PLOTS] amtrak coast starlight 2200km journey takes roughly 35hr for estimated 62km per hr 
```{r}
# All three 
coastStarlight %>% ggplot(aes(x = timeDate, y = distanceKM, group = trainID, color = direction)) +
  geom_line() +
  scale_x_datetime(date_breaks = "4 hour", date_labels = "%a - %H:%M") +
  theme_minimal(base_size = 10) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position = "",
        axis.text.x = element_text(size = 6, angle = 90, vjust = 0, hjust = 0),
        axis.text.y = element_text(size = 6)) +
  labs(x = "",
       y = "",
       title = "Weekly Amtrak Coast Starlight Schedule") + 
  scale_y_reverse(breaks = yAxisStarlight$distanceKM, labels = yAxisStarlight$stationCode, guide = guide_axis(angle = 0, n.dodge = 2, position = "left"))

# Only Urban
coastStarlightLargePop %>% ggplot(aes(x = timeDate, y = distanceKM, group = trainID, color = direction)) +
  geom_line() +
  scale_x_datetime(date_breaks = "4 hour", date_labels = "%a - %H:%M") +
  theme_minimal(base_size = 10) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position = "",
        axis.text.x = element_text(size = 6, angle = 90, vjust = 0, hjust = 0),
        axis.text.y = element_text(size = 8)) +
  labs(x = "",
       y = "",
       title = "Weekly Amtrak Coast Starlight Schedule",
       subtitle = "Cities where population is greater than 200,000") + 
  scale_y_reverse(breaks = yAxisStarlightLargePop$distanceKM, labels = yAxisStarlightLargePop$stop, guide = guide_axis(angle = 25, n.dodge = 1, position = "left"))
# First of the week
coastStarlightMiniOne %>% ggplot(aes(x = timeDate, y = distanceKM, group = trainID, color = direction)) + # group by train add label
  geom_line() +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%a - %H:%M") +
  theme_minimal(base_size = 10) + 
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position  = "",
        legend.direction = "horizontal",
        axis.text.x = element_text(size = 6, angle = 90, vjust = 0, hjust = 0),
        axis.text.y = element_text(size = 6)) +
  labs(x = "",
       y = "",
       title = "Monday/Tuesday Amtrak Schedule") + 
  scale_y_reverse(breaks = yAxisStarlight$distanceKM, labels = yAxisStarlight$stationCode, guide = guide_axis(angle = 0, n.dodge = 2, position = "left"))

# Second of the week
coastStarlightMiniTwo %>% ggplot(aes(x = timeDate, y = distanceKM, group = trainID, color = direction)) + # group by train add label
  geom_line() +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%a - %H:%M") +
  theme_minimal(base_size = 10) + 
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position  = "",
        legend.direction = "horizontal",
        axis.text.x = element_text(size = 6, angle = 90, vjust = 0, hjust = 0),
        axis.text.y = element_text(size = 6)) +
  labs(x = "",
       y = "",
       title = "Wednesday/Thursday Amtrak Schedule") + 
  scale_y_reverse(breaks = yAxisStarlight$distanceKM, labels = yAxisStarlight$stationCode, guide = guide_axis(angle = 0, n.dodge = 2, position = "left"))

# Third of the week
coastStarlightMiniTwo %>% ggplot(aes(x = timeDate, y = distanceKM, group = trainID, color = direction)) + # group by train add label
  geom_line() +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%a - %H:%M") +
  theme_minimal(base_size = 10) + 
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position  = "",
        legend.direction = "horizontal",
        axis.text.x = element_text(size = 6, angle = 90, vjust = 0, hjust = 0),
        axis.text.y = element_text(size = 6)) +
  labs(x = "",
       y = "",
       title = "Friday/Saturday/Sunday Amtrak Schedule for Large Cities") + 
  scale_y_reverse(breaks = yAxisStarlight$distanceKM, labels = yAxisStarlight$stationCode, guide = guide_axis(angle = 0, n.dodge = 2, position = "left"))
```

## interactive plot using plotly of amtrak journey
## need to use a fixed frame because the POSIXct date type is broken with ggplot: https://github.com/ropensci/plotly/issues/1246
## We see how without the actually location of the train at every given time, these long-lat plots are not the most helpful.
## For a nicely done visualization of long-lat over time see: http://senseable.mit.edu/trainsofdata/
```{r}
# add coordinate information to the train time table dataset
coastStarLightInteractive <- merge(coastStarlight, westCoastStationComplete %>% select(stop, lat, long, city), by = "stop", all = FALSE, sort = FALSE)


# create ggplot object
westCoastPlotInteractive <- ggplot(coastStarLightInteractive, aes(x = long, y = lat)) + 
                geom_polygon(data = westCoastMap, aes(x = long, y = lat, group = group), ## make the map plot
                              color = "black", fill = "white") +
                coord_fixed() + 
                geom_point(aes(frame = animationFrame, ids = trainID, color = direction, text=sprintf("Stop: %s<br>Day: %s<br>Time: %s", stop, day, time)), size = 1) +
                theme_void() + 
                 labs(x = "",
                       y = "",
                       title = "Amtrak Coast Starlight Stations") +
                 theme(plot.title = element_text(hjust = 0.5),
                       legend.position = "")

# convert from ggplot to plotly
westCoastGGPlotly <- ggplotly(westCoastPlotInteractive) %>% 
                     animation_opts(500, easing = "elastic", redraw = FALSE) %>% 
                     animation_button(x = 1, xanchor = "left", y = 0, yanchor = "bottom") %>%
                     animation_slider(currentvalue = list(prefix = "Frame", font = list(color="black")))
westCoastGGPlotly
```


## set up shinkansen datasets
```{r}
# shinkansen westbound data
tokyoToHakata <- read.csv("datasets/jr/shinkansenWestbound.csv")
tokyoToHakata <- tokyoToHakata %>% 
  mutate(time = as.POSIXct(time, format = '%H:%M'))

# shinkansen eastbound data
hakataToTokyo <- read.csv("datasets/jr/shinkansenEastbound.csv")
hakataToTokyo <- hakataToTokyo %>% 
  mutate(time = as.POSIXct(time, format = '%H:%M'))

# combine the data
shinkansen <- rbind(tokyoToHakata, hakataToTokyo)

# get the distances from tokyo station
shinkansenStations <- read.csv("datasets/jr/shinkansenDistances.csv")

# get location and population information
shinkansenStationLocationPopulation <- read.csv("datasets/jr/stationLocationPopulation.csv")
shinkansenStationLocationPopulation <- shinkansenStationLocationPopulation %>% rename(stop = station)

shinkansenStations <- shinkansenStations %>% 
  rename(stop = Station_Name, distanceFromToyko = Distance.from.Tokyo.st, line = Shinkansen_Line) %>% 
  select(stop, distanceFromToyko, line) %>%
  mutate_all(funs(tolower)) %>%
  mutate(distanceFromToyko = as.numeric(distanceFromToyko))
  

shinkansen <- shinkansen %>% 
  rename(id = train.id, type = train.type)

shinkansen <- merge(shinkansen, shinkansenStations, by = "stop", all = FALSE, sort = FALSE)
shinkansen <- merge(shinkansen, shinkansenStationLocationPopulation, by = "stop", all = FALSE, sort = FALSE)
shinkansenStationInformation <- merge(shinkansenStationLocationPopulation, shinkansenStations, by = "stop", all = FALSE, sort = FALSE) %>% slice(2:35)

# ensure that it doesn't get blurry when printing the labels.
yAxisShinkansen <- shinkansen %>%
  select(distanceFromToyko, stop) %>%
  unique()
```

# plot the shinkansen stations
```{r}
# get the map data
jp <- map_data("japan")

# osm shinkansen for the prefectures
# OSM CALL 
tokyoRail <- getbb("Tokyo Japan") %>%
    opq(timeout = 20*100) %>%
    add_osm_feature(key = "railway", value = "rail") %>%
    osmdata_sf()

# plot the stations along the tokyo-hakata route
shinkansenPlotLarge <- ggplot() + 
                 geom_polygon(data = jp, aes(x = long, y = lat, group = group), 
                              color = "black", fill = "white") + 
                 coord_fixed() +
                 geom_point(data = shinkansenStationInformation, aes(x = long, y = lat, color = prefecture), 
                            shape = 20, size = 3) +
                 theme_void() + 
                 geom_text_repel(data = shinkansenStationInformation, 
                            aes(x = long, y = lat, label = stop, color = prefecture), 
                            hjust = 1, vjust = 0, size = 2.5,
                            box.padding = 0.20, point.padding = .2, segment.size = 0.2, direction = "x", 
                            nudge_y = -5, angle = 90) + 
                  labs(x = "",
                       y = "",
                       title = "JR Tokyo to Hakata Shinkansen Stations") +
                  theme(plot.title = element_text(hjust = 0.5),
                        legend.position = "",
                        plot.title.position = "panel") +
                  ylim(30, 37) + xlim(130, 142) 


# central japan plot
centralJapan <- shinkansenStationInformation %>% filter(prefecture == "tokyo" | 
                                                        prefecture == "kanagawa" | 
                                                        prefecture == "shizuoka" | 
                                                        prefecture == "aichi" |
                                                        prefecture == "gifu" |
                                                        prefecture == "shiga")

tokyoMap <- map_data("japan") %>% filter(region == "Tokyo" | region == "Kanagawa" | region == "Shizuoka" | region == "Aichi" |
                                         region == "Gifu" | region == "Shiga") 

tokyoPlot <- ggplot() + 
                  geom_polygon(data = tokyoMap, aes(x = long, y = lat, group = group), 
                              color = "black", fill = "white") +
                  coord_fixed() +
                  geom_sf(data = tokyoRail$osm_lines,
                            inherit.aes = FALSE,
                            color = "lightgrey",
                            size = .5,
                            alpha = .6) + 
                  geom_point(data = centralJapan, 
                            aes(x = long, y = lat, color = prefecture,), 
                            shape = 20, size = 2) +
                  geom_text_repel(data = centralJapan, 
                            aes(x = long, y = lat, label = stop, color = prefecture), 
                            hjust = 1, vjust = 0, size = 2.5,
                            nudge_y = -2,
                            box.padding = 0.20, point.padding = .2, segment.size = 0.2, direction = "y", angle = 0) + 
                  theme_void() +   
                  labs(x = "",
                       y = "",
                       title = "JR Shinkansen Stations (Central Japan)") +
                  theme(plot.title = element_text(hjust = 0.5),
                        legend.position = "") +
                  ylim(33.5, 36) + xlim(136, 140)+
                 scale_color_brewer(palette = "Dark2")
```





## [PLOT] shinkansen tokyo to fukuoka: 1196km journey takes 5 hours for estimated 240km per hr
```{r}
shinkansen %>% ggplot(aes(x = time, y = distanceFromToyko, group = id, color = type)) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%H:%M") +
  theme_minimal(base_size = 10) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.direction = "horizontal") +
  labs(x = "",
       y = "",
       title = "Morning Shinkansen Schedule") + 
  scale_y_reverse(limits = c(1200, 0), breaks = yAxisShinkansen$distanceFromToyko, labels = yAxisShinkansen$stop, guide = guide_axis(n.dodge=3)) +
  scale_color_brewer(palette = "Set1") +
```

## compare the shinkansen with coast starlight
```{r}
## Seattle-Portland versus Tokyo-Nagoya
tokyoToNagoya <- shinkansen %>% filter(distanceFromToyko < 350)
tokyoToNagoya <- tokyoToNagoya %>% 
                  mutate(distanceKM = distanceFromToyko) %>% 
                  mutate(line = ifelse(line == "shinkansen", "shinkansen", "shinkansen")) %>%
                  mutate(direction = ifelse(direction == "east", "up", "down")) %>%
                  select(stop, time, direction, distanceKM, line, id)

seattleToPortland <- coastStarlightMiniOne %>% filter(distanceKM < 350)
seattleToPortland <- seattleToPortland %>% 
                      mutate(line = "amtrak") %>% 
                      mutate(direction = ifelse(direction == "toSeattle", "up", "down")) %>%
                      mutate(time = as.POSIXct(time, format = '%H:%M')) %>%
                      mutate(id = trainID) %>%
                      select(stop, time, direction, distanceKM, line, id)

under350KMComparison <- rbind(tokyoToNagoya, seattleToPortland)

under350KMComparison %>% ggplot(aes(x = time, y = distanceKM, group = id, color = direction)) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%H:%M") +
  theme_minimal(base_size = 10) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position = "",
        legend.direction = "horizontal",
        axis.text.x = element_text(size = 6, angle = 90, vjust = 0, hjust = 0),
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "",
       y = "distance",
       title = "Seattle-Portland (301km) Compared with Tokyo-Nagoya (336km)") + 
  scale_y_reverse(limits = c(350, 0)) +
  scale_color_brewer(palette = "Set1") + 
  facet_grid(. ~ line, scale = "fixed")

## Bay Area-Los Angeles versus Tokyo to Okayam
tokyoToOkayama <- shinkansen %>% filter(distanceFromToyko < 750)
tokyoToOkayama <- tokyoToOkayama %>% 
                  mutate(distanceKM = distanceFromToyko) %>% 
                  mutate(line = ifelse(line == "shinkansen", "shinkansen", "shinkansen")) %>%
                  mutate(direction = ifelse(direction == "east", "up", "down")) %>%
                  select(stop, time, direction, distanceKM, line, id)

sfToLA <- coastStarlightMiniOne %>% 
            mutate(distanceKM = distanceKM - 1469) %>%
            filter(distanceKM < 750 & distanceKM > -1)
sfToLA <- sfToLA %>% 
            mutate(line = "amtrak") %>% 
            mutate(direction = ifelse(direction == "toSeattle", "up", "down")) %>%
            mutate(time = as.POSIXct(time, format = '%H:%M')) %>%
            mutate(id = trainID) %>%
            select(stop, time, direction, distanceKM, line, id)

soCal750KMComparison <- rbind(tokyoToOkayama, sfToLA)
soCal750KMComparison %>% ggplot(aes(x = time, y = distanceKM, group = id, color = direction)) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 hour", date_labels = "%H:%M") +
  theme_minimal(base_size = 10) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#cac5c0", linetype = 1),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "#FFFFFF"),
        legend.title = element_blank(),
        legend.position = "",
        legend.direction = "horizontal",
        axis.text.x = element_text(size = 6, angle = 90, vjust = 0, hjust = 0),
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "",
       y = "distance",
       title = "Bay Area-Los Angeles (747km) Compared with Tokyo-Okayama (732.9km)") + 
  scale_y_reverse(limits = c(750, 0)) +
  scale_color_brewer(palette = "Set1") + 
  facet_grid(. ~ line, scale = "fixed")
```

